An overview of the oolong package.

### 2020-07-01 overview_gh.Rmd

Currently, oolong cannot generate topic intrusion tests for Biterm Topic Model.

```{r btm1}
require(BTM)
oolong_test <- create_oolong(abstracts_btm)
oolong_test
```

```{r btm2, error = TRUE}
oolong_test <- create_oolong(abstracts_btm, abstracts$text)
oolong_test
```

>>>>

Please refer to the vignette about BTM.
